### 2020-08-05 docs/msc_thesis_figures.Rmd
updates

```{r message=TRUE, warning=TRUE}
source('~/Documents/Master/Thesis/land_con_monteregie/scripts/functions/draw_scenario.R')
for (scenario in c(39, 42, 45, 48, 51)){
  the_plot <- draw_scenario(scenario, mxp = mxp)
  the_name <- paste0("scenario_", as.character(scenario),"_compare.png")
  ggsave(plot = the_plot, 
         filename = paste0("../thesis/figures/",the_name), width = 20, height = 10, dpi = the_dpi)
}

>>>>

```{r message=FALSE, warning=FALSE}
source('~/Documents/Master/Thesis/land_con_monteregie/scripts/functions/draw_scenario.R')
for (scenario in c(39, 42, 45, 48, 51)){
  the_plot <- draw_scenario(scenario, mxp = mxp)
  the_name <- paste0("scenario_", as.character(scenario),"_compare.png")
  ggsave(plot = the_plot, 
         filename = paste0("../thesis/figures/",the_name), width = 30, height = 12, dpi = the_dpi)
}

### 2020-08-05 thesis/appendix_1.tex
updates

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/BAU_compare.png}
}
 \caption{Comparison of Monteregie at the beginning of the BAU simulation in 2010, and at the end in 2100 (BAU-Baseline scenario).}
 \label{fig:BAU_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/Ref_compare.png}
}
 \caption{Comparison of Monteregie at the beginning of the Reforestation simulation in 2010, and at the end in 2100 (BAU-Reforestion-Baseline scenario).}
 \label{fig:Ref_compare}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/Corr_compare.png}
}
 \caption{Corr).}
 \label{fig:Corr_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/CorrRef_compare.png}
}
 \caption{CorrRef).}
 \label{fig:	CorrRef_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/CorrRefTar_compare.png}
}
 \caption{CorrRefTar.}
 \label{fig:	CorrRefT_compare}
\end{figure}

>>>>

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_39_compare.png}
}
 \caption{Comparison of Monteregie at the beginning of the BAU simulation in 2010, and at the end in 2100 (BAU-Baseline scenario).}
 \label{fig:BAU_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_42_compare.png}
}
 \caption{Comparison of Monteregie at the beginning of the Reforestation simulation in 2010, and at the end in 2100 (BAU-Reforestion-Baseline scenario).}
 \label{fig:Ref_compare}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_45_compare.png}
}
 \caption{Corr).}
 \label{fig:Corr_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_48_compare.png}
}
 \caption{CorrRef).}
 \label{fig:	CorrRef_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_51_compare.png}
}
 \caption{CorrRefTar.}
 \label{fig:	CorrRefT_compare}
\end{figure}
